A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-28 writeup/paper.tex

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{final-figures/turkermap}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of  5,284 workers in our study.  The size of the circles represents the number of workers from each country.  The two largest are India (2,017 workers) and the United States (904).  To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure}[h]
\centering
%\includegraphics[height=\linewidth,angle=270]{figures/completetime}
\includegraphics[height=\linewidth,angle=270]{final-figures/completetime}
\caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
\label{completion-time}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% ASSIGNMENT SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{final-figures/assign-turk-scatter}
\caption{Number of assignments and number of Turkers for each language. Each dot represents a language. Figure includes only data from Turkers who reported only one native language consistantly across assignments, representing approx. 3900 turkers across 139,000 assignments.}
\label{ass-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{final-figures/google-match-bar}
\caption{Translation quality of by source language. Blue bars show quality estimates by language and green bars show proportion of translations which matched Google Translate. Total quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-
pass HIT. Dark blue bars indicate the proportion of translations which exactly matched known translations, and light blue indicate translations which were judged to be correct synonyms. Quality estimates are only show for languages with at least 50 active turkers.}
\label{hitlangqual-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{final-figures/quality-scatter}
\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. Quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT. Figure represents data from approx. 295,000 assignments for which geolocation was known.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of  5,284 workers in our study.  The size of the circles represents the number of workers from each country.  The two largest are India (2,022 workers) and the United States (904).  To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure}[h]
\centering
%\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
\includegraphics[height=\linewidth,angle=270]{figures/completiontime-new}
\caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
\label{completion-time}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% ASSIGNMENT SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/assign-turk-scatter-new}
\caption{Number of assignments and number of Turkers for each language. Each dot represents a language. Figure includes only data from Turkers who reported only one native language consistantly across assignments, representing approx. 3900 turkers across 139,000 assignments.}
\label{ass-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-hitlang-goog}
\caption{Translation quality of by source language. Blue bars show quality estimates by language and green bars show proportion of translations which matched Google Translate. Total quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-
pass HIT. Dark blue bars indicate the proportion of translations which exactly matched known translations, and light blue indicate translations which were judged to be correct synonyms. Quality estimates are only show for languages with at least 50 active turkers.}
\label{hitlangqual-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-scatter}
\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. Quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT. Figure represents data from approx. 281,000 assignments for which geolocation was known.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
